Lattice Boltzmann simulations of magnetically responsive\\ ellipsoidal particle stabilized emulsions

### 2025-03-19 chapters/final_remarks.tex
Changes 1. Adapted conclusion to new aim 3 text

In Aim 1, bijels stabilized with spherical particles do not respond to the application of a magnetic field. However, bijels stabilized
with ellipsoidal particles have an increase in the average domain size by 3 \%. The microstructure also becomes anisotropic, 
characterized as a change in the directional tortuosity and distribution of channel widths as a function of the distance from the 
interface. The response characterized was particle morphology specific due to the orientation of the particle magnetic moment with 
respect to the direction of the long axis of the particle. This causes the particles to arrange differently on the interface. The 
microstructure anisotropy is caused by direction specific jamming of the particle monolayer originating from particle ordering to 
the magnetic field. The direction specific jamming originates from the orientation of the particles to the magnetic field. The direction
specific jamming also reduces the local curvature of the system as the interface location moves with the particle.

To investigate the role of the particle monolayer in greater detail, we characterize the orientational order to the magnetic field,
angle to the interface and local particle ordering at the interface. The orientational order changes as a function of the applied field 
strength and has particle morphology specific time evolution. When investigating the average interfacial angle of the particles to the 
interface, it is shown how the capillary interactions with the interface differ, leading to the time evolution differences observed.
When analyzing the ordering of particles on the interface, disc-like particles see lowered local ordering as the magnetic field strength is 
increased while rod-like particles see greater local ordering. These properties are attributed to how those particle morphologies prefer 
to orient themselves at interfaces to one another, with disc like particles preferring to stack while rod like particles order side to side 
or end to end.

In Aim 2, bijels stabilized by ellipsoidal particles demonstrate responses to an applied magnetic field. When applying a magnetic field
onto a bijel template simulated with no magnetic fields, we see an average microstructure change of up to 5 \%. This microstructure change
arises from the magnetic field driven re-orientation of particles at the interface. Particle reorientation creates microstructure anisotropy
arising from the alignment of particles to the magnetic field. When analyzing the particle monolayer, we characterize the alignment of particles
to the field direction, average interface angle and the local ordering of the particles. We demonstrate that the average interface angle increases
as the particles reorient to the field before the capillary forces of the interfaces causes the interface to move, until jamming of the monolayer takes
place. The local particle order during this process decreases for oblate particles and increases for prolate particles. We characterize that the local 
order of the particles controls the timescales of response.

When investigating the effect of pre-existing order of the particle monolayer, we show that the structural response of the bijel is dependent upon the
difference between the field applied to make the bijel and the applied field when the field is applied in the same direction. We also characterize that the
local particle monolayer is dependent upon the pre-existing order of the bijel. When switching off the magnetic field onto bijels made with a magnetic field,
we see that the microstructure remains resilient to the removal of the magnetic field. We characterize that while there are differences in the particle monolayer,
these differences manifest as when domain coarsening begins. When characterizing the hysteresis curve of the bijels stabilized with prolate particles,
we see the effect of this.

In Aim 3 we investigate the rheological response of bijels stabilized with ellipsoidal particles under constant shear and show that the application of magnetic
fields changes the shear thinning properties of bijels.

>>>>

In Aim 1, bijels stabilized with spherical particles do not respond to the application of a magnetic field. However, bijels stabilized
with ellipsoidal particles have an increase in the average domain size by 3 \%. The microstructure also becomes anisotropic, 
characterized as a change in the directional tortuosity and distribution of channel widths as a function of the distance from the 
interface. The response characterized was particle morphology specific due to the orientation of the particle magnetic moment with 
respect to the direction of the long axis of the particle. This causes the particles to arrange differently on the interface. The 
microstructure anisotropy is caused by direction specific jamming of the particle monolayer originating from particle ordering to 
the magnetic field. The direction specific jamming originates from the orientation of the particles to the magnetic field. The direction
specific jamming also reduces the local curvature of the system as the interface location moves with the particle.
To investigate the role of the particle monolayer in greater detail, we characterize the orientational order to the magnetic field,
angle to the interface and local particle ordering at the interface. The orientational order changes as a function of the applied field 
strength and has particle morphology specific time evolution. When investigating the average interfacial angle of the particles to the 
interface, it is shown how the capillary interactions with the interface differ, leading to the time evolution differences observed.
When analyzing the ordering of particles on the interface, disc-like particles see lowered local ordering as the magnetic field strength is 
increased while rod-like particles see greater local ordering. These properties are attributed to how those particle morphologies prefer 
to orient themselves at interfaces to one another, with disc like particles preferring to stack while rod like particles order side to side 
or end to end.

In Aim 2, bijels stabilized by ellipsoidal particles demonstrate responses to an applied magnetic field. When applying a magnetic field
onto a bijel template simulated with no magnetic fields, we see an average microstructure change of up to 5 \%. This microstructure change
arises from the magnetic field driven re-orientation of particles at the interface. Particle reorientation creates microstructure anisotropy
arising from the alignment of particles to the magnetic field. When analyzing the particle monolayer, we characterize the alignment of particles
to the field direction, average interface angle and the local ordering of the particles. We demonstrate that the average interface angle increases
as the particles reorient to the field before the capillary forces of the interfaces causes the interface to move, until jamming of the monolayer takes
place. The local particle order during this process decreases for oblate particles and increases for prolate particles. We characterize that the local 
order of the particles controls the timescales of response.
When investigating the effect of pre-existing order of the particle monolayer, we show that the structural response of the bijel is dependent upon the
difference between the field applied to make the bijel and the applied field when the field is applied in the same direction. We also characterize that the
local particle monolayer is dependent upon the pre-existing order of the bijel. When switching off the magnetic field onto bijels made with a magnetic field,
we see that the microstructure remains resilient to the removal of the magnetic field. We characterize that while there are differences in the particle monolayer,
these differences manifest as when domain coarsening begins. When characterizing the hysteresis curve of the bijels stabilized with prolate particles,
we see the effect of this.

In Aim 3, I investigated the rheology of bijels stabilized by ellipsoidal particles under shear, examining the effects of initial microstructure and a 
constant magnetic field on their shear response. Using a Herschel-Bulkley fitting, I found that while shear-thinning behavior remains robust, the 
flow index and yield stress are strongly influenced by particle morphology and magnetic field application. Increased particle ordering led to 
lower yield stress in oblate-particle-stabilized bijels and higher yield stress in prolate-particle-stabilized bijels, highlighting the role of particle 
shape in interfacial mechanics. Without a magnetic field, both particle monolayers remained adsorbed at the interface, but when a field was applied, 
oblate particles flipped out of the interface, whereas prolate particles tilted, altering the flow field and impacting non-Newtonian behavior. Additionally, 
coarsening driven by reduced interfacial particle coverage emerged as the dominant mechanism behind domain size evolution in sheared bijels. The anisotropic 
domain growth trends matched expectations in all cases except when the field was removed, indicating that the history of field application significantly influences 
microstructural evolution. These findings provide insight into the interplay between particle morphology, interfacial coverage, and external fields, contributing 
to the understanding of magnetically tunable soft materials and structured emulsions.
